Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
Fix minor latex mistakes
figure env -> table env again

\subsection{Software Corpus}
\begin{table}
\centering
\sisetup{
  table-format = 7,
  table-number-alignment = right
}
\begin{tabular}{|l|S|S|S|}
\hline
Package       & {Files} & {Lines of code} & {Files analysed} \\ % braces prevent headers from being formatted as numbers
\hline
UM            & \umFiles & \umLoC & \umparseOk  \\
E3MG          & \ethreemgeaFiles   & \ethreemgeaLoC & \ethreemgeaparseOk  \\
BLAS          & \blasFiles   & \blasLoC & \blasparseOk        \\
Hybrid4       & \hybridfourFiles    & \hybridfourLoC & \hybridfourparseOk         \\
GEOS-Chem     & \geoschemFiles   & \geoschemLoC & \geoschemparseOk       \\
Navier        & \navierFiles     & \navierLoC & \navierparseOk           \\
CP            & \computationalphysicstwoFiles    & \computationalphysicstwoLoC & \computationalphysicstwoparseOk           \\
\hline
\textbf{Total}& \overallFiles  & \overallLoC   & \overallparseOk  \\
\hline
\end{tabular}
\caption{Summary of software packages used for evaluation\label{tab:corpus}}
\end{table}

@@

\begin{figure}
\begin{tabular}{|l|l|l|l|l|}
\hline
Package       & Potential & Actual & Exact & Inexact    \\
\hline
UM            & \umtickAssign\ (\umtickAssignPercent\%) &
                \umtickAssignSuccess\ (\umtickAssignSuccessPercent\%) &
                \umnumStencilLines &
                \umboundedBoth  \\
E3MG          & \ethreemgeatickAssign\ (\ethreemgeatickAssignPercent\%) &
                \ethreemgeatickAssignSuccess\ (\ethreemgeatickAssignSuccessPercent\%) &
                \ethreemgeanumStencilLines &
                \ethreemgeaboundedBoth \\
BLAS          & \blastickAssign\ (\blastickAssignPercent\%) &
                \blastickAssignSuccess\ (\blastickAssignSuccessPercent\%) &
                \blasnumStencilLines &
                \blasboundedBoth \\
Hybrid4       & \hybridfourtickAssign\ (\hybridfourtickAssignPercent\%) &
                \hybridfourtickAssignSuccess\ (\hybridfourtickAssignSuccessPercent\%) &
                \hybridfournumStencilLines &
                \hybridfourboundedBoth\\
GEOS-Chem     & \geoschemtickAssign\ (\geoschemtickAssignPercent\%) &
                \geoschemtickAssignSuccess\ (\geoschemtickAssignSuccessPercent\%) &
                \geoschemnumStencilLines &
                \geoschemboundedBoth \\
Navier        & \naviertickAssign\ (\naviertickAssignPercent\%) &
                \naviertickAssignSuccess\ (\naviertickAssignPercent\%) &
                \naviernumStencilLines &
                \navierboundedBoth \\
CP            & \computationalphysicstwotickAssign\ (\computationalphysicstwotickAssignPercent\%) &
                \computationalphysicstwotickAssignSuccess\ (\computationalphysicstwotickAssignSuccessPercent\%) &
                \computationalphysicstwonumStencilLines &
                \computationalphysicstwoboundedBoth \\
\hline
\textbf{Total}& \overalltickAssign\ (\overalltickAssignPercent\%)  &
                \overalltickAssignSuccess\ (\overalltickAssignSuccessPercent\%) &
                \overallnumStencilLines &
                \overallboundedBoth    \\
\hline
\end{tabular}
\caption{Stencil assignment rates\label{fig:tickAssign}}
\end{figure}

The first two columns of Figure \ref{fig:tickAssign} shows the number of potential and actual stencils and their rate as a percentage of the total number of assignment statements in the code. There are a variety of reasons why we might not infer an actual stencil from a potential one: 1) \textbf{Non-subset induction variables} occurs when the induction variables on the RHS are not a subset of the LHS. These cases are not stencils by our definition. The degenereate case of this is to have only constant indices on the LHS. We see lots of examples of this in loops as accumulators e.g. computing the sum over some other array; 2) \textbf{Derived induction variables} where the indexing variable (\mintinline{fortran}{x}) is derived from an induction variable \mintinline{fortran}{i} e.g. \mintinline{fortran}{x = len - i}; 3) \textbf{Inconsistent induction dimensions} occur when an induction variable is used to specify more than one array dimension on the RHS. These are common in matrix operations such as LU-decomposition which contains assignments such as \mintinline{fortran}{a(l) = a(l) - a(m) * b(l, m)}.

>>>>

\subsection{Software Corpus}
\begin{table}
\centering
\sisetup{
  table-format = 7,
  table-number-alignment = right
}
\begin{tabular}{|l|S|S|S|}
\hline
Package   & {Files} & {Files analysed} & {Lines of code}  \\ % braces prevent headers from being formatted as numbers
\hline
UM        & \umFiles                       & \umparseOk                      & \umLoC                     \\
E3MG      & \ethreemgeaFiles               & \ethreemgeaparseOk              & \ethreemgeaLoC             \\
BLAS      & \blasFiles                     & \blasparseOk                    & \blasLoC                   \\
Hybrid4   & \hybridfourFiles               & \hybridfourparseOk              & \hybridfourLoC             \\
GEOS-Chem & \geoschemFiles                 & \geoschemparseOk                & \geoschemLoC               \\
Navier    & \navierFiles                   & \navierparseOk                  & \navierLoC                 \\
CP        & \computationalphysicstwoFiles  & \computationalphysicstwoparseOk & \computationalphysicstwoLoC\\
\hline
\textbf{Total} & \overallFiles  & \overallparseOk & \overallLoC  \\
\hline
\end{tabular}
\caption{Summary of software packages used for evaluation\label{tab:corpus}}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|l|l|l|l|}
\hline
{Package}     & {Potential} & {Actual} & {Exact} & {Inexact}    \\
\hline
UM            & \umtickAssign\ (\umtickAssignPercent\%) &
                \umtickAssignSuccess\ (\umtickAssignSuccessPercent\%) &
                \umnumStencilLines &
                \umboundedBoth  \\
E3MG          & \ethreemgeatickAssign\ (\ethreemgeatickAssignPercent\%) &
                \ethreemgeatickAssignSuccess\ (\ethreemgeatickAssignSuccessPercent\%) &
                \ethreemgeanumStencilLines &
                \ethreemgeaboundedBoth \\
BLAS          & \blastickAssign\ (\blastickAssignPercent\%) &
                \blastickAssignSuccess\ (\blastickAssignSuccessPercent\%) &
                \blasnumStencilLines &
                \blasboundedBoth \\
Hybrid4       & \hybridfourtickAssign\ (\hybridfourtickAssignPercent\%) &
                \hybridfourtickAssignSuccess\ (\hybridfourtickAssignSuccessPercent\%) &
                \hybridfournumStencilLines &
                \hybridfourboundedBoth\\
GEOS-Chem     & \geoschemtickAssign\ (\geoschemtickAssignPercent\%) &
                \geoschemtickAssignSuccess\ (\geoschemtickAssignSuccessPercent\%) &
                \geoschemnumStencilLines &
                \geoschemboundedBoth \\
Navier        & \naviertickAssign\ (\naviertickAssignPercent\%) &
                \naviertickAssignSuccess\ (\naviertickAssignPercent\%) &
                \naviernumStencilLines &
                \navierboundedBoth \\
CP            & \computationalphysicstwotickAssign\ (\computationalphysicstwotickAssignPercent\%) &
                \computationalphysicstwotickAssignSuccess\ (\computationalphysicstwotickAssignSuccessPercent\%) &
                \computationalphysicstwonumStencilLines &
                \computationalphysicstwoboundedBoth \\
\hline
\textbf{Total}& \overalltickAssign\ (\overalltickAssignPercent\%)  &
                \overalltickAssignSuccess\ (\overalltickAssignSuccessPercent\%) &
                \overallnumStencilLines &
                \overallboundedBoth    \\
\hline
\end{tabular}
\caption{Stencil assignment rates\label{tab:tickAssign}}
\end{table}

The first two columns of Table~\ref{tab:tickAssign} shows the number of potential and actual stencils and their rate as a percentage of the total number of assignment statements in the code. There are a variety of reasons why we might not infer an actual stencil from a potential one: 1) \textbf{Non-subset induction variables} occurs when the induction variables on the RHS are not a subset of the LHS. These cases are not stencils by our definition. The degenereate case of this is to have only constant indices on the LHS. We see lots of examples of this in loops as accumulators e.g. computing the sum over some other array; 2) \textbf{Derived induction variables} where the indexing variable (\mintinline{fortran}{x}) is derived from an induction variable \mintinline{fortran}{i} e.g. \mintinline{fortran}{x = len - i}; 3) \textbf{Inconsistent induction dimensions} occur when an induction variable is used to specify more than one array dimension on the RHS. These are common in matrix operations such as LU-decomposition which contains assignments such as \mintinline{fortran}{a(l) = a(l) - a(m) * b(l, m)}.
